
%\RequirePackage{fix-cm}
\documentclass{article}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amsmath,amssymb}



\begin{document}




\begin{thebibliography}{}
  \bibitem[ASC20]{ASC}
    Paul Apisa, Rafael M. Saavedra, Christopher Zhang:
    \newblock{Periodic points on the regular and double n-gon surfaces}.
    \newblock{arXiv:2011.02668 (2020)}%.


\newpage
  \bibitem[HS07]{HS3}  Herrlich, F.,  Schmith\"usen, G.:
    \newblock{ A comb of origami curves in $M_3$}.
    \newblock{Geom.\ Dedicata, \textbf{124}, 69--94 (2007)}
  \bibitem[T12]{Tsu}
    角皆 宏:
    \newblock{種数 1 の Grothendieck dessin の計算}.
    \newblock{数理解析研究所講究録 \textbf{1813}, 167--182 (2012)}%.
%books
\bibitem{A} L. V. Ahlfors,
\newblock{\it Lectures on Quasiconformal Mappings},
\newblock{Amer. Math. Soc., Providence, RI, (1966)}%. MR2241787

%Journal Reference
\bibitem{EG} C. J. Earle, F. P. Gardiner, 
\newblock{\it Teichm{\"u}ller disks and Veech's $\mathcal{F}$-Structures},
\newblock{Contemp. Math. \textbf{201}, 165--189 (1997)}%. %MR1429199

%Journal Reference
\bibitem{EM} J. Ellenberg, D. B. McReynolds, 
\newblock{\it Arithmetic Veech sublattices of $\mathrm{SL}(2,\mathbb{Z})$},
\newblock{Duke Math. J. \textbf{161}, no. 3, 415--429 (2012)}%. %MR2881227

%books
\bibitem{Ga} F. P. Gardiner, N. Lakic, 
\newblock{\it Quasiconformal Teichm{\"u}ller Theory},
\newblock{Amer. Math. Soc., Providence, RI, (2000)}%.% MR1730906

%Journal Reference
\bibitem{GJ} E. Gutkin, C. Judge, 
\newblock{\it Affine mappings of translation surfaces: Geometry and arithmetic},
\newblock{Duke Math. J. \textbf{103}, no. 2, 191--213 (2000)}%. %MR1760625

%Journal Reference
\bibitem{H} F. Herrlich, G. Schmith\"usen,
\newblock{\it A comb of origami curves in $M_3$},
\newblock{Geom. Dedicata, \textbf{124}, 69--94 (2007)}%. MR2318538

%Journal Reference
\bibitem{HS1} F. Herrlich, G. Schmith\"usen,
\newblock{\it Dessins d'enfants and origami curves},
\newblock{IRMA Lect. Math. Theor. Phys., \textbf{13}, 767--809 (2009)}%. MR2516744

%Journal Reference
\bibitem{HS2} F. Herrlich, G. Schmith\"usen,
\newblock{\it An extraordinary origami curve},
\newblock{Math. Nachr. \textbf{281}, No.2, 219--237 (2008)}%. MR 2387362


%books
\bibitem{IT} Y. Imayoshi, M. Taniguchi, 
\newblock{\it An Introduction to Teichm{\"u}ller Space},
\newblock{Springer-Verlag, Tokyo (1992)}%. MR1215481

%Journal Reference
\bibitem{L} P. Lochak, 
\newblock{\it On arithmetic curves in the moduli spaces of curves},
\newblock{J. Inst. Math. Jussieu \textbf{4}, no. 3, 443--508 (2005)}%. MR2197065

%\bibitem{MKS} W. Magnus, A. Karrass, D. Solitar, 
%\newblock{\it Combinatorial group theory},
%\newblock{Dover Publications, Inc., Mineola, NY, 2004}. MR2109550

%Journal Reference
\bibitem{M1} M. M{\"o}ller,
\newblock{\it Teichm{\"u}ller curves, Galois actions and $\widehat{GT}$-relations},
\newblock{Math. Nachr. \textbf{278}, no.9, 1061--1077 (2005)}%. MR2150378

%Journal Reference
\bibitem{M2} M. M{\"o}ller,
\newblock{\it Variations of Hodge structures of a Teichm\"uller curve},
\newblock{J. Amer. Math. Soc. \textbf{19}, no.2, 327--344 (2006)}%. MR2188128

%Journal Reference
\bibitem{S1} G. Schmith\"usen,
\newblock{\it An algorithm for finding the Veech group of an origami},
\newblock{Experiment. Math. \textbf{13}, no. 4, 459--472 (2004)}%. MR2118271

%Journal Reference
\bibitem{Sh} Y. Shinomiya, 
\newblock{\it Veech groups of flat structures on {R}iemann surfaces},
\newblock{Contemp. Math. \textbf{575}, 343--362 (2012)}%. MR2933909

%books
\bibitem{St} K. Strebel, 
\newblock{\it Quadratic Differentials},
\newblock{Springer-Verlag, Berlin, Heidelberg (1984)}%. 

%Journal Reference
\bibitem{V} W. Veech,
\newblock{\it Teichm\"uller curves in moduli space, Eisenstein series and an application to triangular billiards},
\newblock{Invent. Math. \textbf{97}, no.4, 553--584 (1989)}%. 
  
% etc

\end{thebibliography}
\end{document}
% end of file template.tex

